---
title: "MBTI_test"
author: "Zhilin Kong"
date: '2022-06-12'
output: 
  pdf_document:
         latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data
```{r}
library(ggplot2)
Gender = c(rep("Male",5),rep("Female",5))
Q2 = c(5,4,4,3,3,4,4,3,3,2)
Q3 = c(5,4,2,3,2,3,2,2,2,2)
Q4 = c(4,4,3,3,3,3,4,4,2,4)
Q5 = c(4,3,3,4,3,4,4,4,3,5)
Q6 = c(3,4,4,4,2,4,4,4,4,2)
Q7 = c(4,4,4,4,2,3,4,3,4,4)
Q8 = c(5,5,3,4,3,5,4,3,3,4)
Q9 = c(4,4,5,4,4,4,4,4,5,5)
Q10 = c(4,4,2,4,3,4,4,4,5,3)
Q11 = c(4,4,4,4,3,3,4,3,5,3)
Q12 = c(5,5,5,4,5,5,5,4,5,5)
Q13 = c(4,5,4,4,5,4,4,3,5,4)
df = data.frame(Gender,factor(Q2),
                Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13);df
matrix = cbind(Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13)
boxplot(matrix, col = "pink")
```

## Boostrapping (vs. MBTI resutls)
## H0: The Survey's result agrees with the MBTI's result.
## H1: The Survey's result doesn't agree with the MBTI's result.
```{r}
library(boot)
#Observed Test Statistic
scale = c(1,2,3,4,5)
Mind = 3 - abs(3-quantile(scale,probs=0.67)[[1]]);Mind #vs. Q3
Energy = quantile(scale,probs=0.59)[[1]];Energy #vs.Q5
Nature = quantile(scale,probs=0.75)[[1]];Nature #vs. Q4
Tactics = quantile(scale,probs=0.74)[[1]];Tactics #vs. Q6
Identity = quantile(scale,probs=0.67)[[1]]; Identity #vs.Q7

#Random Sampling Function.
# data: the data where the sample is from.
# i: index
#Return the mean of each sample.
function1 = function(data,i) {
  d = data[i]
  return (mean(d))
}

#Bootstrapping function to find confidence interval(CI) and give conclusion.
#vec: the bootstrapping vector.
#obs: the observed statistic.
#print: Boolean variable. True:print the bootstrap statistics and CI;   False:otherwise.
#question: a string. the question's number.
#return a string, a conclusion based on the test result.
boot_function = function(vec, obs, print,question){
  results = boot(data=vec,statistic=function1,R=1000)
  ci = boot.ci(results,type="basic")

  if(print){
    print(results)
    print(ci)
  }
  
  lower = ci$basic[4]
  upper = ci$basic[5]
  if (obs >= lower & obs<= upper){
    str = paste(question,"failed to reject the H0.")
  }
  else{
    str = paste(question, "rejects the H0.")
  }
  return (str)
}
#For readers' reference
boot_function(Q3,Mind,TRUE,'Q3')
boot_function(Q5,Energy,F,'Q5')
boot_function(Q4,Nature,F,'Q4')
boot_function(Q6,Tactics,F,'Q6')
boot_function(Q7,Identity,F,'Q7')
```
Conclusion:
Q3 Introverted vs. Extroverted -> Both agree: Introverted$\\$
Q5 Idealism vs. Pragmatism -> Both agree: Pragmatism$\\$
Q4 Emotional vs. Rational -> Disagree$\\$
Q6 Disorganized vs. Organized -> Both agree: Organized$\\$
Q7 Self-abased vs. Confident -> Both agree: Confident$\\$

## Another way to use bootstrapping(for reader who is interested)
```{r}
set.seed(123)
x = 1:30
boot_mean = c()
for (i in 1:1000){
  resam = base::sample(x,size=length(x),replace=TRUE)
  mu = mean(resam)
  boot_mean = append(boot_mean,mu)
}
hist(boot_mean)
quantile(boot_mean, probs=c(0.025,0.975))
```

## Test whether there is a different criteria for two genders.
## H0: They have the same criteria.
## H1: They have different criterion.
## The grade's mean for each question
```{r}
mu_each_question = c(colMeans(matrix));mu_each_question
#sort in ascending order.
sort(mu_each_question)
```

## calculate the means of two genders.
```{r}
#Get rid of column "Q2"
mat = matrix[,2:12] #or using mat=matrix[,colnames(matrix)!="Q2"]
Female_mean = colMeans(mat[6:10,]);Female_mean
Male_mean = colMeans(mat[1:5,]);Male_mean
```

## A more general way to calculate the means is by using group_by method.
```{r}
library(dplyr)
Qlist = c(Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13)
df1 = df %>% group_by(Gender)%>%summarise(mean_Q3 = mean(Q3),
                                          mean_Q4 = mean(Q4),
                                          mean_Q5 = mean(Q5),
                                          mean_Q6 = mean(Q6),
                                          mean_Q7 = mean(Q7),
                                          mean_Q8 = mean(Q8),
                                          mean_Q9 = mean(Q9),
                                          mean_Q10 = mean(Q10),
                                          mean_Q11 = mean(Q11),
                                          mean_Q12 = mean(Q12),
                                          mean_Q13 = mean(Q13),.groups = 'drop')
df1
```

## Applying t.test
```{r}
library(ggstatsplot)
matrix.t = cbind(Male_mean,Female_mean);matrix.t
t.test(Male_mean,Female_mean,paired=TRUE)
```
p.value = 0.8963 > $\alpha = 0.05$. Therefore, I failed to reject the $H_0$.

## Or applying the non-parametric test:Wilcoxon signed-rank test
```{r}
wilcox.test(Male_mean,Female_mean,paired=TRUE,exact=F,correct=F)
```
p.value = 0.888 > $\alpha = 0.05$. Therefore, again, I failed to reject the $H_0$.

Conclusion:
Based on this sample, I failed to reject the H0: males and females have the same judgement.


## parametric version (for your reference)
```{r}
  ggbetweenstats(data = df,x = Gender,y = Q3,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q4,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q5,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q6,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q7,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q8,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q9,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q10,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q11,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q12,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
  ggbetweenstats(data = df,x = Gender,y = Q13,
                 plot.type = "box",type = "parametric",centrality.plotting = FALSE)
```

## The non-parametric version
```{r}
ggbetweenstats(data = df,x = Gender,y = Q3,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q4,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q5,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q6,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q7,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q8,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q9,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q10,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q11,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q12,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
ggbetweenstats(data = df,x = Gender,y = Q13,
               plot.type = "box",type = "nonparametric",centrality.plotting = FALSE)
```
Conclusion:
Based on this sample, for every question, I failed to reject the H0 again: the males and the females have the same criteria.
